SI_ExtraPlots

### 2020-08-12 analysis/4_extra_plots/SI_extraplots.Rmd
port old plotting code to backup

>>>>

### Analyze detections around naming events (without posture/orientation)

```{r include=FALSE}
# difference plots can be confusing, ommitting
# faces_namings_diffs_indiv <- aroundNamings_Detections_BySub_Fam_Faces_All %>%
#   spread(familiarity, prop_detected) %>%
#   mutate(fam_dif = familiar - baseline, nov_diff = novel - baseline) 
#
# ggplot(faces_namings_diffs_indiv, aes(x=age.grp, y=nov_diff, group=age.grp)) +
#   geom_boxplot() +
#   theme_few()

## explored looking at namings while acconting for posture and orientation
# aroundNamings_Detections_BySub_Posture_Faces <- aroundNamings_Faces %>%
#   group_by(subid, familiarity, posture, orientation, age.grp) %>%
#   summarize(prop_detected = mean(detections, na.rm=TRUE)) %>%
#   mutate(detectorType = 'OpenPose-Wrists')
# 
# baseline_diffs_by_posture <- dlong %>%
#   filter(detectorType == 'OpenPose-Wrists') %>%
#   group_by(age.grp, subid, posture, orientation,detectorType) %>%
#   summarise(prop_detected = mean(detection)) %>%
#   mutate(familiarity = 'baseline') %>%
#   full_join(aroundNamings_Detections_BySub_Posture_Faces)
# 
# naming = lmer(data = aroundNamings_Detections_BySub_Posture_Faces, prop_detected ~ familiarity + posture * orientation + (1|subid))
# summary(naming)
```

```{r setUpNamingsPlot}

## first get baseline
# baselineFaces <- dlongPlot %>%
#   filter(detectorType == 'OpenPose-Faces') %>%
#   group_by(age.grp, subid, detectorType) %>%
#   summarise(prop_detected = mean(detection)) %>%
#   mutate(familiarity='baseline')
# 
# baselineWrists <- dlongPlot %>%
#   filter(detectorType == 'OpenPose-Wrists') %>%
#   group_by(age.grp, subid, detectorType) %>%
#   summarise(prop_detected = mean(detection)) %>%
#   mutate(familiarity='baseline')
# 
# 
# ### then by faces
# aroundNamings_Detections_BySub_Faces <- aroundNamings_Faces %>%
#   group_by(subid, familiarity, age.grp) %>%
#   summarize(prop_detected = mean(detections, na.rm=TRUE)) %>%
#   mutate(detectorType = 'OpenPose-Faces') %>%
#   full_join(baselineFaces)
# 
# aroundNamings_Detections_Grouped_Faces <- aroundNamings_Detections_BySub_Faces %>%
#   group_by(familiarity, age.grp) %>%
#   multi_boot_standard(col = 'prop_detected')  
# 
# ### now by wrists 
# aroundNamings_Detections_BySub_Wrists <- aroundNamings_Wrists %>%
#   group_by(subid, familiarity, age.grp) %>%
#   summarize(prop_detected = mean(detections, na.rm=TRUE)) %>%
#   mutate(detectorType = 'OpenPose-Wrists') %>%
#   full_join(baselineWrists)
# 
# aroundNamings_Detections_Grouped_Wrists <- aroundNamings_Detections_BySub_Wrists %>%
#   group_by(familiarity, age.grp) %>%
#   multi_boot_standard(col = 'prop_detected')

```{r detByNamingPlotPanels}
## Plot faces/wrists around namings by age

# faces_aroundnamings_plot <- ggplot(aroundNamings_Detections_Grouped_Faces, aes(x=age.grp, y=mean, color=familiarity)) +
#   # plot averages by familiarity 
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width=2), alpha=.9) +
#   # plot familairity detections for each sub
#   geom_point(data=aroundNamings_Detections_BySub_Faces, aes(x=age.grp, y=prop_detected), position = position_dodge(width=2), alpha=.2) +
#   theme_few() +
#   labs(y = "Prop. face detections", x = "Age (months)") +
#   theme_few(base_size=plot_size) +
#   ylim(0,.4) +
#   theme(legend.position="bottom", legend.text=element_text(size = 12), legend.margin=margin(t=0, r=0, b=0, l=0, unit="cm"), legend.title=element_text(size = 14)) +
#   scale_colour_viridis(name = 'Object familiarity', discrete=TRUE, option='A', begin=.2, end=.8) +
#   scale_x_continuous(breaks=seq(8, 16, 4), limits=c(7, 18))

## 
# wrists_aroundnamings_plot <- ggplot(aroundNamings_Detections_Grouped_Wrists, aes(x=age.grp, y=mean, color=familiarity)) +
#   # plot averages by familiarity 
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width=2), alpha=.9) +
#   # plot familairity detections for each sub
#   geom_point(data=aroundNamings_Detections_BySub_Wrists, aes(x=age.grp, y=prop_detected), position = position_dodge(width=2), alpha=.2) +
#   theme_few() +
#   labs(y = "Prop. wrist detections", x = "Age (months)") +
#   theme_few(base_size=plot_size) +
#   ylim(0,.4) +
#   theme(legend.position="bottom", legend.text=element_text(size = 12), legend.margin=margin(t=0, r=0, b=0, l=0, unit="cm"), legend.title=element_text(size = 14)) +
#   scale_colour_viridis(name = 'Object familiarity', discrete=TRUE, option='A', begin=.2, end=.8) +
#   scale_x_continuous(breaks=seq(8, 16, 4), limits=c(7, 18)) 
```
